---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PCD

<!-- badges: start -->
<!-- badges: end -->

The goal of PCD is to make it easier to work with the Provisional COVID-19 Death Counts by Sex, Age, and State published by the CDC at https://dev.socrata.com/foundry/data.cdc.gov/9bhg-hcku

The package invokes a REST API to get the latest data from the CDC. For details on the data elements, please visit the CDC page at: https://dev.socrata.com/foundry/data.cdc.gov/9bhg-hcku 

## Installation

You can install the released version of PCD from [CRAN](https://CRAN.R-project.org) with:

``` r
devtools::install_github("atsats/PCD")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(PCD)
## The code below fetches up to 1,000 records for the State of New Jersey.
cdc_data <- getpcd(maxrecs=1000,state="New%20Jersey")
## The latest entire data set can be retrieved with
cdc_data <- getpcd(maxrecs=5000)
```

Here's a sample usage of the package. 

```{r cars}
# Get the national-level data
cdc_data <- getpcd(maxrecs=1000,state="United%20States")
# filter the columns of interest (note that CDC's age_category overlap, so eliminate the overlaps)
d <- cdc_data[cdc_data$state == "United States" & cdc_data$sex == "All Sexes" & cdc_data$age_group %in% c("15-24 years","25-34 years","35-44 years","45-54 years","55-64 years","65-74 years","75-84 years","85 years and over") & is.na(cdc_data$year) ,]
# focus on the important variables
f <- data.frame(age_group=d$age_group,covid_19_deaths= d$covid_19_deaths,total_deaths=d$total_deaths)
(f)
```


